Update of the ozone dry deposition in the OsloCTM3 v1.0

### 2018-10-18 DryDep.tex
Updated tree_heights.pdf. Spell checked text. Not much more progress, since I have to figure out impact of viscosity parameterization...

with a temperature dependent absolute viscosity of air $\mu(T) = 6.2\cdot 10^{-8}\,\unit{mol \, m^{-2} s^{-1} K^{-1}} \cdot T$ \citep{PBL} ($\{T \in \mathbb{R} | (233 < T < 303)\,\unit{K}\}$) and substituting the air density $\rho$ using the ideal gas law. $P_0$ is the surface pressure, as $T$ the 2\,\unit{m} temperature is chosen, and $R_\text{air}$ the universal gas constant for air.

@@

wherein $F_N = 3$ for fine nitrate and ammonium and $F_N = 1$ for all other species and $L$ is again the Obukhov length. $a_2 = 300\,\unit{m}$, while $a_1$ differes for forest and non-forest. To account for hydrophilic and hydrophobic BC/OC aerosols on dry and wet surfaces, we diverge slightly from the EMAP scheme in the definition of the parameter $a_1$. From pre-studies with an aerosol microphysic model, we find

>>>>

with a temperature dependent dynamic viscosity of air $\mu(T) = 6.2\cdot 10^{-8}\,\unit{kg \, m^{-1} s^{-1} K^{-1}} \cdot T$ \citep{PBL} ($\{T \in \mathbb{R} | (243.15 < T < 313.15)\,\unit{K}\}$) and substituting the air density $\rho$ using the ideal gas law. $P_0$ is the surface pressure, as $T$ the 2\,\unit{m} temperature is chosen, and $R_\text{air}$ the universal gas constant for air.

@@

wherein $F_N = 3$ for fine nitrate and ammonium and $F_N = 1$ for all other species and $L$ is again the Obukhov length. $a_2 = 300\,\unit{m}$, while $a_1$ differs for forest and non-forest. To account for hydrophilic and hydrophobic BC/OC aerosols on dry and wet surfaces, we diverge slightly from the EMAP scheme in the definition of the parameter $a_1$. From pre-studies with an aerosol microphysic model, we find
